---
title: "Network Analysis"
author: "Nehemiah Ongeso"
date: "29/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## lOAD REQUIRED PACKAGES

```{r}
#install.packages(c('tidyverse','gplots','ggplot2','knitr','limma','reshape2','RColorBrewer'))

#BiocManager:install(c('WGCNA','limma','OrganismDbi','dupRadar','Rsubread','edgeR','sva','reshape2','ggfortify','flashClust','igraph','RCy3'))

library('gplots')
library('ggplot2')
#library('knitr')
library('limma')
library('reshape2')
library('RColorBrewer')
library('WGCNA')
library('tidyverse')
#library('RCy3')
library('edgeR')
#library('OrgabismDbi')
#library('dupRadar')
library('Rsubread')
#library('sva')
library('reshape2')
library('ggfortify')
library('flashClust')
library('igraph')
```

```{r}
# Make sure results are reproducible
set.seed(1)

options(stringsAsFactors=FALSE);
# Allowing multi-threading within WGCNA speeds up certain calculations
enableWGCNAThreads(nThreads=200) 
# Read sample meta-data file
samples <- read.csv('/data/nongeso/nongeso/nehe/data_r/metadata.csv', header=TRUE)

#kable(samples)

samples$condition<-factor(samples$condition)

samples$condition

# Read in count data
raw_counts <- read.table('/data/nongeso/nongeso/nehe/data_r/NA.txt', row.names=1, header=TRUE)
head(raw_counts)
dim(raw_counts)

names(raw_counts)
raw_counts<-raw_counts[-c(1:5),]


names(raw_counts)<- c("Egg_2","J3_3","J4_3","J4_2","Egg_1","J4_1",
                      "Adult_2","Adult_1","Adult_3","J2_2","J3_1","J2_3","J3_2","J2_1","Egg_3")
```

```{r}
# Data Preparation
# Sample check
# add a colorbar along the heatmap with sample condition

sizeGrWindow(9, 5)
par(mfrow = c(1,2));
cex1 = 0.9;
num_conditions <- nlevels(samples$condition)
pal <- colorRampPalette(brewer.pal(num_conditions, "Set1"))(num_conditions)
cond_colors <- pal[as.integer(samples$condition)]

result<- "/data/nongeso/nongeso/nehe/GCN_Finale_Analysis/GCN_Plant_Parasite_Interaction/results"
setwd(result)

sizeGrWindow(9, 6)
par(mfrow = c(1,2));
cex1 = 0.9;
png("1.Raw_Correlations.png")
heatmap.2(cor(raw_counts), RowSideColors=cond_colors,
          trace='none', main='Raw Correlations')
dev.off()
```
```{r}
#Low count filtering
# Remove all rows with less than n counts across all samples, where n=#samples

# from the edger package
keep.exprs <- filterByExpr(raw_counts, group=samples$condition)
filtered_raw_counts <- raw_counts[keep.exprs,]
dim(filtered_raw_counts)
dim(raw_counts)

#LOG2 TRANSFORMATION
# Most of the methods developed for co-expression network analysis and network
# inference were written for use with micro array data, 
# including WGCNA!

# Attempting to apply a method such as this to discrete-count 
# RNA-Seq data will not work out well.

# There are a number of methods for working around this, in effect, 
# making RNA-Seq data "look" more like microarray data, 
# but the simplest thing is just to log the data. 
# This will transform our discrete, over-dispersed counts 
# to a more Poisson-like continuous distribution.

log_counts <- log2(filtered_raw_counts + 1)
head(log_counts)

log_counts <- log_counts[apply(log_counts, 1, var) > 0,]
dim(log_counts)

# Let's see how things look after logging the data.

x = melt(as.matrix(log_counts))

colnames(x) = c('gene_id', 'sample', 'value')
ggplot(x, aes(x=value, color=sample)) + geom_density()

heatmap.2(cor(log_counts), RowSideColors=cond_colors,
          trace='none', main='Sample correlations (log2-transformed)')

```
```{r}
# CO-EXPRESSION NETWORK CONSTRUCTION
# First, build a similarity matrix

# Construct similarity matrix
# Now, we are ready to start constructing our co-expression network. The first step is to generate a correlation, 
# or more generally, a similarity matrix.
# Here, we will use a metric that I have created which combines some of the benefits from both Pearson correlation and Euclidean Distance
#' Similarity measure which combines elements from Pearson correlation and
#' Euclidean distance.

cordist <- function(dat) {
  cor_matrix  <- cor(t(dat))
  
  dist_matrix <- as.matrix(dist(dat, diag=TRUE, upper=TRUE))
  dist_matrix <- log1p(dist_matrix)
  dist_matrix <- 1 - (dist_matrix / max(dist_matrix))
  
  sign(cor_matrix) * ((abs(cor_matrix) + dist_matrix)/ 2)
}

sim_matrix <- cordist(log_counts)
# Let's see what our similarity matrix looks like at this point. Because the heatmap.2 function (which includes a biclustering step) 
# can be pretty slow, we will use a sub-sample of our data -- for visualization purposes this is fine.


heatmap_indices <- sample(nrow(sim_matrix), 500)

heatmap.2(t(sim_matrix[heatmap_indices, heatmap_indices]),
          col=redgreen(75),
          labRow=NA, labCol=NA, 
          trace='none', dendrogram='row',
          xlab='Gene', ylab='Gene',
          main='Similarity matrix',
          density.info='none', revC=TRUE)
```
```{r}
# transpose the matrix before constructing an adjacency matrix
log_counts_t <- t(log_counts)
head(log_counts_t)
#view(log_counts_t) 

# Construct similarity matrix
# determine the soft-thresholding power to use

powers <- c(c(1:10), seq(from = 12, to=30, by=2))

# Call the network topology analysis function
sft <- pickSoftThreshold(log_counts_t, powerVector = powers, verbose = 5)
# Plot the results:

sizeGrWindow(9, 6)
par(mfrow = c(1,2));
cex1 = 0.9;
#png("4. soft-thresholding_power.png")

# Scale-free topology fit index as a function of the soft-thresholding power
plot(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     xlab="Soft Threshold (power)",ylab="Scale Free Topology Model Fit,signed R^2",type="n",
     main = paste("Scale independence"));
text(sft$fitIndices[,1], -sign(sft$fitIndices[,3])*sft$fitIndices[,2],
     labels=powers,cex=cex1,col="red");
# this line corresponds to using an R^2 cut-off of h
abline(h=0.5,col="red")
#dev.off()
```

```{r}
# construct adjacency matrix
softpower <- 16
adjacency.matrix <- adjacency(log_counts_t, power=softpower,
                              type = "signed", corFnc = "cor") ###changed corType

```

```{r}
# Turn the adjacency matrix to topologicaal overlap matrix to minimize
# the effects of noise and spurious associations
TOM <- TOMsimilarity(adjacency.matrix, TOMType = "signed")
dissTOM <- 1 - TOM


#set diagonal to NA to remove uninformative correlations
diag(adjacency.matrix) <- NA

# Adjacency matrix heatmap plot / network heatmap of selected genes
heatmap_indices <- sample(nrow(adjacency.matrix), 500) # sub-sample for visualization purposes

png("6. adjacency_matrix_heatmap.png")
heatmap.2(t(adjacency.matrix[heatmap_indices, heatmap_indices]),
          col=redgreen(75),
          labRow=NA, labCol=NA, 
          trace='none', dendrogram='row',
          xlab='Gene', ylab='Gene',
          main='Adjacency matrix',
          density.info='none', revC=TRUE)
dev.off()
```

```{r}

# remove adjacency matrix and TOM to free up memory
rm(adjacency.matrix)
gc()

```

```{r}
################################################################
## Detecting co-expression modules in R
################################################################

# view the dendrogram based on hierachical clustering of genes
gene_tree <- flashClust(as.dist(dissTOM), method = "average")

# plot the gene tree
png("7. gene_tree.png")
#sizeGrWindow(12,9) #open graphical window
plot(gene_tree, xlab="", sub="", main = "Gene clustering based on TOM dissimilarity", 
     labels = FALSE, hang = 0.04)
dev.off()

```


```{r}
# identify the modules
module_labels <- cutreeDynamicTree(gene_tree, deepSplit = FALSE, 
                                   minModuleSize = 30)

#view
table(module_labels)

# convert labels to colours
module_colours <- labels2colors(module_labels)

# view
table(module_colours)

#### a list of 110 modules#

```


```{r}
# visualize the gene tree and TOM matrix together using TOM plot
# if necessary, raise dissTOM to a power to make moderately strong connection more visible in heatmap
diag(dissTOM) <- NA

png("8. gene_tree_and_dissTOM.png")
TOMplot(dissTOM, gene_tree, as.character(module_colours))
dev.off()
# remove matrix to free memory
rm(dissTOM)
gc()
```


```{r}
# plot gene dendrogram
png(filename = "9. gene_tree_and_colours.png")
#sizeGrWindow(8,6) #open graphical window
plotDendroAndColors(gene_tree, module_colours, "Dynamic Tree Cut", dendroLabels = FALSE,
                    hang = 0.03, addGuide = TRUE, guideHang = 0.05,
                    main = "Gene dendrogram and module colours")
dev.off()
```

```{r}
# get hub genes
# choose power 4: https://support.bioconductor.org/p/46342/
module_hub_genes <- chooseTopHubInEachModule(log_counts_t, module_colours, 
                                             power = 4,type = "signed")


#saveRDS(module_hub_genes, file = here::here("data","intermediate","module_hub_genes.RDS"))
length(module_hub_genes)
module_hub_genes         ## add this
##### A list of module hub genes#

#The section below is included for further checks so it may not be necessary to carry out this analysis.

# --------------------------------------------------------------------------------------------
# merge modules with very similar expression profiles as their genes are highly co-expressed
# get the module eigengenes
module_eigengenes <- moduleEigengenes(log_counts_t, colors = module_colours)$eigengenes

# calculate dissimilarity of module eigengenes using correlations
module_eigengenes_diss <- 1 - cor(module_eigengenes)

# cluster module eigengenes
module_eigengenes_tree <- flashClust(as.dist(module_eigengenes_diss), method = "average")

# choose height at which to cut the tree for merge i.e. the threshold
module_eigengenes_thresh <- 0.25

# create plots for the results
png("10. module_eigengenes_cluster.png")
#sizeGrWindow(7, 6)
plot(module_eigengenes_tree, main = "Clustering of module eigengenes", xlab = "", sub = "")
abline(h=module_eigengenes_thresh, col="red")

dev.off()

# merge the modules
module_eigengenes_merge <- mergeCloseModules(log_counts_t, module_colours, 
                                             cutHeight = module_eigengenes_thresh)

# merged module colours
merged_module_colours <- module_eigengenes_merge$colors
length(merged_module_colours)
# view
table(merged_module_colours)

### a list of 16 modules


# eigengenes of new merged modules
merged_module_eigengenes <- module_eigengenes_merge$newMEs


# plot the dendrogram with original and merged colours underneath
#sizeGrWindow(12, 9)
png("11. merged-original_colours-original_dendro.png")
plotDendroAndColors(gene_tree, cbind(module_colours, merged_module_colours), 
                    c("Dynamic Tree Cut", "Merged dynamic"), 
                    dendroLabels = FALSE, hang = 0.03, addGuide = TRUE, guideHang = 0.05)
dev.off()

# plot heatmap of eigengenes (orginal before merge)
png("12. eigengenes_heatmap.png")
plotEigengeneNetworks(module_eigengenes, "Eigengenes heatmap", marHeatmap = c(3,4,2,2),
                      plotDendrograms = FALSE, xLabelsAngle = 90)
dev.off()



#-----------------------------------------------------------------------------------------
# rename some variables based on the module eigengene analysis for later use
#
# module colours
#module.colours <- merged.module.colours

# construct numerical labels corresponding to the colours
colorOrder <- c("grey", standardColors(50))
#module.labels <- match(module.colours, colorOrder)-1

# module eigengenes
#module.eigengenes <- merged.module.eigengenes

# get hub genes
merged_module_hub_genes <- chooseTopHubInEachModule(log_counts_t,
                                                    merged_module_colours,
                                                    power = 4,
                                                    type = "signed")

merged_module_hub_genes ###add this
#### a list of merged module hub genes#

##############################################################################
## Network export to cytoscape
##############################################################################

# select modules of interest

interesting_modules <- c('antiquewhite2', 'antiquewhite4', 'bisque4', 'black', 'blue','blue2', 'blue4', 
                         'blueviolet', 'brown', 'brown2','brown4', 'coral', 'coral1', 'coral2', 'coral3', 
                         'cyan', 'darkgreen', 'darkgrey', 'darkmagenta','darkolivegreen', 'darkolivegreen2', 
                         'darkolivegreen4', 'darkorange', 'darkorange2', 'darkred', 'darkseagreen3', 'darkseagreen4', 
                         'darkslateblue', 'darkturquoise', 'darkviolet', 'deeppink', 'firebrick3', 'firebrick4', 'floralwhite',
                         'green', 'greenyellow', 'grey60', 'honeydew', 'honeydew1', 'indianred3', 'indianred4', 'ivory', 
                         'lavenderblush2', 'lavenderblush3', 'lightblue4', 'lightcoral','lightcyan', 'lightcyan1', 'lightgreen', 
                         'lightpink3', 'lightpink4', 'lightslateblue', 'lightsteelblue', 'lightsteelblue1', 'lightyellow', 'magenta',
                         'magenta4', 'maroon', 'mediumorchid', 'mediumpurple1', 'mediumpurple2', 'mediumpurple3', 'mediumpurple4', 
                         'midnightblue', 'navajowhite1', 'navajowhite2', 'orange', 'orangered1', 'orangered3', 'orangered4', 
                         'paleturquoise', 'palevioletred2', 'palevioletred3', 'pink', 'pink4', 'plum', 'plum1', 'plum2', 
                         'plum3', 'plum4', 'purple', 'red', 'royalblue', 'saddlebrown', 'salmon', 'salmon1', 'salmon2', 
                         'salmon4', 'sienna3', 'sienna4', 'skyblue', 'skyblue1', 'skyblue2', 'skyblue3', 'skyblue4', 
                         'steelblue', 'tan', 'tan4', 'thistle', 'thistle1', 'thistle2', 'thistle3', 'thistle4', 
                         'turquoise', 'violet', 'white', 'yellow', 'yellow3', 'yellow4', 'yellowgreen') # all 110 module colours, thus the whole network




interesting_modules_1 <- c('antiquewhite4', 'bisque4','blue4','blueviolet', 'coral', 'darkgreen','darkolivegreen',
                           'darkolivegreen4', 'darkorange', 'darkorange2', 'darkseagreen4','firebrick4', 'floralwhite',
                           'green', 'greenyellow', 'grey60', 'honeydew', 'indianred4', 'ivory', 'lavenderblush3', 'lightgreen', 
                           'lightpink4', 'lightsteelblue', 'lightyellow', 'magenta4','mediumorchid', 'mediumpurple1', 'mediumpurple2', 
                           'mediumpurple4', 'midnightblue', 'navajowhite2', 'orangered1', 'orangered4', 'paleturquoise', 
                           'palevioletred2', 'palevioletred3', 'pink', 'pink4', 'plum4', 'purple', 'red', 'royalblue', 
                           'salmon1', 'salmon2', 'salmon4', 'sienna3', 'skyblue', 'skyblue1', 
                           'steelblue', 'tan4', 'thistle', 'thistle1', 'thistle2', 'thistle3', 'thistle4', 
                           'turquoise', 'yellow') # all 61 module colours, thus the whole network


interesting_modules_2<-c('salmon2', 'salmon4', 'sienna3', 'skyblue', 'skyblue1',
                         'steelblue', 'tan4', 'thistle', 'thistle1', 'thistle2', 'thistle3', 'thistle4',
                         'turquoise', 'yellow')


# obtain gene ids
gene_ids <- rownames(log_counts)

# select module genes
#inModules <- is.finite(match(module.colours, interesting.modules)) # whole network modules

#inModules <- is.finite(match(module.colours, enriched.modules)) # enriched modules
#inModules <- is.finite(match(module_colours, c("midnightblue", "lightcyan"))) # individual modules
inModules <- is.finite(match(module_colours, interesting_modules )) # whole network modules
inModules61 <- is.finite(match(module_colours, interesting_modules_1 )) # 61 network modules
inModule_few<- is.finite(match(module_colours, interesting_modules_2 )) # 61 network modules
modGenes <- gene_ids[inModules]
modGenes61 <- gene_ids[inModules61]
modGenes_few <- gene_ids[inModules_few]



# select the corresponding dissTOM based on module genes
modTOM <- TOM[inModules, inModules]
modTOM61 <- TOM[inModules61, inModules61]
modTOM_few <- TOM[inModules_few, inModules_few]

dimnames(modTOM) <- list(modGenes, modGenes)
dimnames(modTOM61) <- list(modGenes61, modGenes61)
dimnames(modTOM_few) <- list(modGenes61, modGenes_few)


# Export the network into edge and node list files Cytoscape can read


exportNetworkToCytoscape(modTOM,
                         edgeFile = "CytoscapeInput-edges_wh_module_thresh03.txt",
                         nodeFile = "CytoscapeInput-nodes_wh_module_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGenes,
                         nodeAttr = module_colours[inModules]);




exportNetworkToCytoscape(modTOM61,
                         edgeFile = "CytoscapeInput-edges_61_module_thresh3.txt",
                         nodeFile = "CytoscapeInput-nodes_61_module_thresh3.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGenes61,
                         nodeAttr = module_colours[inModules61]);

exportNetworkToCytoscape(modTOM61,
                         edgeFile = "CytoscapeInput-edges_61_module_thresh1.txt",
                         nodeFile = "CytoscapeInput-nodes_61_module_thresh1.txt",
                         weighted = TRUE,
                         threshold = 0.1,
                         nodeNames = modGenes61,
                         nodeAttr = module_colours[inModules61]);

exportNetworkToCytoscape(modTOM_few,
                         edgeFile = "CytoscapeInput-edges_few_module_thresh3.txt",
                         nodeFile = "CytoscapeInput-nodes_few_module_thresh3.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGenes_few,
                         nodeAttr = module_colours[inModules_few]);

# Also, export the network as graphml format
# use export_network_to_graphml function

source("/data/nongeso/nehe/data_r/network_export_graphml.R")#####

# the whole network
entire_network <- export_network_to_graphml(TOM, 
                                            filename = "entire_network_thresh0.graphml",
                                            threshold = 0, #### why not 0.4
                                            nodeAttr = gene_ids,
                                            max_edge_ratio = 3)


# the whole network
entire_network <- export_network_to_graphml(TOM, 
                                            filename = "entire_network_thresh02.graphml",
                                            threshold = 0.3, #### why not 0.4
                                            nodeAttr = gene_ids,
                                            max_edge_ratio = 3)


# network modules
# create a dataframe with node attributes
interesting_modules_colours <- module_colours[inModules] #get enriched module colours from module.colours
interesting_modules_colours61 <- module_colours[inModules61] #get enriched module colours from module.colours
interesting_modules_colours_few <- module_colours[inModules_few] #get enriched module colours from module.colours

node_attributes <- cbind(modGenes, module=interesting_modules_colours) # node atrr. for enriched modules
node_attributes61 <- cbind(modGenes61, module=interesting_modules_colours61) # node atrr. for enriched modules
node_attributes_few <- cbind(modGenes_few, module=interesting_modules_colours_few) # node atrr.

#node.attributes <- cbind(modGenes, module=module.colours) # get node attr. for whole network
node_attributes <- as.data.frame(node_attributes)
node_attributes61 <- as.data.frame(node_attributes61)
node_attributes_few <- as.data.frame(node_attributes_few)


# Add RGB versions of colour modules
node_attributes$colourRGB <- col2hex(node_attributes$module)
node_attributes61$colourRGB <- col2hex(node_attributes61$module)
node_attributes_few$colourRGB <- col2hex(node_attributes_few$module)

modules_network <- export_network_to_graphml(modTOM, 
                                             filename = "modules_network_thresh0.02.graphml",
                                             threshold = 0.02, ###threshold change ######
                                             nodeAttrDataFrame = node_attributes)



modules_network61 <- export_network_to_graphml(modTOM61, 
                                               filename = "modules_network61_thresh0.02.graphml",
                                               threshold = 0.02, ###threshold change ######
                                               nodeAttrDataFrame = node_attributes61)

# write out a node attributes files with hexadecimal colour names for module genes
write.table(node_attributes, 
            file = "Cytoscape_node_attributes_wh_modules_.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t")


#sd

## Functional Analysis

### Loading annotations from the packages


all_merged_modules
mod1
mod2
mod3
mod4
mod5
mod6
mod7
mod8
mod9
mod10

inModule_merged <- is.finite(match(merged_module_colours, all_merged_modules)) # merged module network
inModule1 <- is.finite(match(merged_module_colours, mod1 )) # modules
inModule2 <- is.finite(match(merged_module_colours, mod2)) # 61 network modules
inModule3 <- is.finite(match(merged_module_colours, mod3 )) # modules
inModule4 <- is.finite(match(merged_module_colours, mod4)) # 61 network modules
inModule5 <- is.finite(match(merged_module_colours, mod5 )) # modules
inModule6 <- is.finite(match(merged_module_colours, mod6)) # 61 network modules
inModule7 <- is.finite(match(merged_module_colours, mod7 )) # modules
inModule8 <- is.finite(match(merged_module_colours, mod8)) # 61 network modules
inModule9 <- is.finite(match(merged_module_colours, mod9 )) # modules
inModule10 <- is.finite(match(merged_module_colours, mod10)) # 61 network modules

modGene_merged <- gene_ids[inModule_merged]
modGene1 <- gene_ids[inModule1]
modGene2 <- gene_ids[inModule2]
modGene3 <- gene_ids[inModule3]
modGene4 <- gene_ids[inModule4]
modGene5 <- gene_ids[inModule5]
modGene6 <- gene_ids[inModule6]
modGene7 <- gene_ids[inModule7]
modGene8 <- gene_ids[inModule8]
modGene9 <- gene_ids[inModule9]
modGene10 <- gene_ids[inModule10]

# select the corresponding dissTOM based on module genes
modTOM_merged <- TOM[inModule_merged, inModule_merged]
modTOM1<- TOM[inModule1, inModule1]
modTOM2<- TOM[inModule2, inModule2]
modTOM3<- TOM[inModule3, inModule3]
modTOM4<- TOM[inModule4, inModule4]
modTOM5<- TOM[inModule5, inModule5]
modTOM6<- TOM[inModule6, inModule6]
modTOM7<- TOM[inModule7, inModule7]
modTOM8<- TOM[inModule8, inModule8]
modTOM9<- TOM[inModule9, inModule9]
modTOM10<- TOM[inModule10, inModule10]

dimnames(modTOM_merged) <- list(modGene_merged ,modGene_merged )
dimnames(modTOM1) <- list(modGene1, modGene1)
dimnames(modTOM2) <- list(modGene2, modGene2)
dimnames(modTOM3) <- list(modGene3, modGene3)
dimnames(modTOM4) <- list(modGene4, modGene4)
dimnames(modTOM5) <- list(modGene5, modGene5)
dimnames(modTOM6) <- list(modGene6, modGene6)
dimnames(modTOM7) <- list(modGene7, modGene7)
dimnames(modTOM8) <- list(modGene8, modGene8)
dimnames(modTOM9) <- list(modGene9, modGene9)
dimnames(modTOM10) <- list(modGene10, modGene10)

exportNetworkToCytoscape(modTOM_merged,
                         edgeFile = "Merged_Modules_Edges_thresh03.txt",
                         nodeFile = "Merged_Modules_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene_merged,
                         nodeAttr = merged_module_colours[inModule_merged]);


exportNetworkToCytoscape(modTOM1,
                         edgeFile = "Modules1_Edges_thresh03.txt",
                         nodeFile = "Modules1_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene1,
                         nodeAttr = merged_module_colours[inModule1]);

exportNetworkToCytoscape(modTOM2,
                         edgeFile = "Modules2_Edges_thresh03.txt",
                         nodeFile = "Modules2_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene2,
                         nodeAttr = merged_module_colours[inModule2]);

exportNetworkToCytoscape(modTOM3,
                         edgeFile = "Modules3_Edges_thresh03.txt",
                         nodeFile = "Modules3_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene3,
                         nodeAttr = merged_module_colours[inModule3]);

exportNetworkToCytoscape(modTOM4,
                         edgeFile = "Modules4_Edges_thresh03.txt",
                         nodeFile = "Modules4_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene4,
                         nodeAttr = merged_module_colours[inModule4]);

exportNetworkToCytoscape(modTOM5,
                         edgeFile = "Modules5_Edges_thresh03.txt",
                         nodeFile = "Modules5_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene5,
                         nodeAttr = merged_module_colours[inModule5]);

exportNetworkToCytoscape(modTOM6,
                         edgeFile = "Modules6_Edges_thresh03.txt",
                         nodeFile = "Modules6_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene6,
                         nodeAttr = merged_module_colours[inModule6]);

exportNetworkToCytoscape(modTOM7,
                         edgeFile = "Modules7_Edges_thresh03.txt",
                         nodeFile = "Modules7_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene7,
                         nodeAttr = merged_module_colours[inModule7]);

exportNetworkToCytoscape(modTOM8,
                         edgeFile = "Modules8_Edges_thresh03.txt",
                         nodeFile = "Modules8_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene8,
                         nodeAttr = merged_module_colours[inModule8]);

exportNetworkToCytoscape(modTOM9,
                         edgeFile = "Modules9_Edges_thresh03.txt",
                         nodeFile = "Modules9_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene9,
                         nodeAttr = merged_module_colours[inModule9]);

exportNetworkToCytoscape(modTOM10,
                         edgeFile = "Modules10_Edges_thresh03.txt",
                         nodeFile = "Modules10_Nodes_thresh03.txt",
                         weighted = TRUE,
                         threshold = 0.3,
                         nodeNames = modGene10,
                         nodeAttr = merged_module_colours[inModule10]);


# network modules
# create a dataframe with node attributes
i_modules_colours_merged <- merged_module_colours[inModule_merged]
i_modules_colours1 <- merged_module_colours[inModule1] 
i_modules_colours2 <- merged_module_colours[inModule2] 
i_modules_colours3 <- merged_module_colours[inModule3] 
i_modules_colours4 <- merged_module_colours[inModule4] 
i_modules_colours5 <- merged_module_colours[inModule5] 
i_modules_colours6 <- merged_module_colours[inModule6] 
i_modules_colours7 <- merged_module_colours[inModule7] 
i_modules_colours8 <- merged_module_colours[inModule8] 
i_modules_colours9 <- merged_module_colours[inModule9] 
i_modules_colours10 <- merged_module_colours[inModule10] 

node_attributes_merged <- cbind(modGene_merged, module=i_modules_colours_merged) # node attr.
node_attributes1 <- cbind(modGene1, module=i_modules_colours_merged) # node attr.
node_attributes2 <- cbind(modGene2, module=i_modules_colours_merged) # node attr.


#node.attributes <- cbind(modGenes, module=module.colours) # get node attr. for whole network
node_attributes_merged <- as.data.frame(node_attributes_merged)
node_attributes1 <- as.data.frame(node_attributes1)
node_attributes2 <- as.data.frame(node_attributes2)
node_attributes3 <- as.data.frame(node_attributes3)
node_attributes4 <- as.data.frame(node_attributes4)
node_attributes5 <- as.data.frame(node_attributes5)
node_attributes6 <- as.data.frame(node_attributes6)
node_attributes7 <- as.data.frame(node_attributes7)
node_attributes8 <- as.data.frame(node_attributes8)
node_attributes9 <- as.data.frame(node_attributes9)
node_attributes10 <- as.data.frame(node_attributes10)


# Add RGB versions of colour modules
node_attributes_merged$colourRGB <- col2hex(node_attributes_merged$module)
node_attributes1$colourRGB <- col2hex(node_attributes1$module)
node_attributes2$colourRGB <- col2hex(node_attributes2$module)
node_attributes3$colourRGB <- col2hex(node_attributes3$module)
node_attributes4$colourRGB <- col2hex(node_attributes4$module)
node_attributes5$colourRGB <- col2hex(node_attributes5$module)
node_attributes6$colourRGB <- col2hex(node_attributes6$module)
node_attributes7$colourRGB <- col2hex(node_attributes7$module)
node_attributes8$colourRGB <- col2hex(node_attributes8$module)
node_attributes9$colourRGB <- col2hex(node_attributes9$module)
node_attributes10$colourRGB <- col2hex(node_attributes10$module)

# write out a node attributes files with hexadecimal colour names for module genes
write.table(node_attributes_merged, 
            file = "Merged_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
# write out a node attributes files with hexadecimal colour names for module genes
write.table(node_attributes1, 
            file = "Module1_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes2, 
            file = "Module2_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes3, 
            file = "Module3_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes4, 
            file = "Module4_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes5, 
            file = "Module5_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes6, 
            file = "Module6_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes7, 
            file = "Module7_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes8, 
            file = "Module8_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes9, 
            file = "Module9_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");
write.table(node_attributes10, 
            file = "Module10_Node_Attributes_modules.txt",
            row.names = FALSE, 
            quote = FALSE, sep = "\t");